---
title: "R_NY"
author: "Tomasz Kisiel"
date: "2024-10-12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This is a simple project aiming to show R skills. Through this project I will share basic skills of loading and formatting data. Multiple tables are joined and grouped in order to present complete summary and explicit statistics. At the end, data are presented in graphics  

Used database is provided with R package for flights departed in 2013 from New York City. 

```{r Reading data, echo=FALSE}
#install.packages("nycflights13")
library(nycflights13)
summary(flights)
summary(airlines)
summary(airports)
summary(planes)
summary(weather)
```
There were 336776 flights. 
The longest one was of 4983 miles but the shortest one was only 17 miles.
The longest time in air was of 695 minutes but the shortest one was only 20 minutes long.
Regarding maximum delay it was of 1301 minutes. On the other hand, the earliest departure was 43 minutes before scheduled time.

Flights were served by 16 carriers.

There were 1458 destinations. 

Through the New York City airport there passed 3322 different planes. 
The oldest one was manufactured in 1956 and the newest one was from 2013.
The largest plane was designed to carry 450 passengers but the smallest one was only for 2.
The average cruising speed was of 236.8 mph.

The strongest wind during take off or landing was 1048 mph but the average one was only 10 mph.
The strongest precipitations were of 1,21 inch.
Mean visibility was of 9,2 miles but the worst one was of 0,0 miles.

## Data correction

This section present data changes in order to facilitate further analysis.

```{r data correction}
na_qty <- sum(is.na(airlines),
    is.na(airports),
    is.na(flights),
    is.na(planes),
    is.na(weather))
na_qty
```

Total quantity of NA values is 73941.

## Data collections

This section present initial grouped statistics.

```{r grouped statistics}
### code to be added

```

## Table join

This section aims to join multiple tables .

```{r table join}
### code to be added

```

## Graphs

This section presents main graphics.

```{r graphs, echo=FALSE}
### code to be added

```

